Between Subgraph Isomorphism and Maximum Common Subgraph

### 2017-01-31 poster/poster.tex
Better hyphening

Given two graphs $G$ and $H$, the \textbf{maximum common subgraph problem} is to find the largest graph which is isomorphic to
a subgraph of both $G$ and $H$ --- the size of the maximum common subgraph gives us a measure of how similar two graphs are.

>>>>

The \textbf{maximum common subgraph problem} is to find the largest graph which is isomorphic to
a subgraph of two graphs simultaneously---the size of the maximum common subgraph gives us a measure of how similar two graphs are.
